Postural changes mediate children's visual access to social information

### 2018-01-14 writeup-cogsci-copy/cogsci2018.Rmd
citation brackets redone

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(lme4)
library(gridExtra)
```
# Introduction
Children are remarkably skilled language learners, connecting arbitrary labels (“cup”) with specific visual concepts at a rapid pace through the first two years of life. However, children do not learn words in a vacuum but in a rich social environment, where social cues provided by speakers (e.g., eye-gaze) provide strong scaffolding for this learning process. Indeed, children’s ability to effectively process these social cues may be a key factor in their early language development. For example,in a longitudinal study, children’s level of joint engagement with their mother was found to predict both their receptive and productive vocabularies (@carpenter1998).  More recently, 10 month-olds who follow an adult’s gaze in an experimental context have larger vocabularies at 18 months (@brooks2005) and throughout the second year of life (@brooks2008).

@@

One possibility is that these motor improvements have strong developmental cascades, impacting children’s emerging social, cognitive, and linguistic abilities (Iverson, 2010). Indeed, these postural changes also impact how children interact with their mothers;  walking infants make different kinds of object-related bids for attention from their mothers than crawling infants, and tend to hear more action directed statements (e.g., “open it”) [@karasik2014].  More directly, in an observational study, @walle2014 found that children who were able to walk had both higher receptive and productive vocabularies.  On their account, children’s ability to stand and independently locomote may fundamentally change their ability to access the social information (e.g., faces, gaze) relative to children who are still crawling and sitting. In other words, the ability to access more detailed social information may allow infants to learn words quicker and more efficiently, facilitating language growth.

Recent work has begun to use egocentric, head-mounted cameras to document the visual experiences of infants and children — which even for walking children are radically different than the adult perspective (and not easily predicted by our own adult intuitions; @franchak2011, @yoshida2008; @clerkin2017). Children’s views tend to be restricted and to be dominated by objects and hands much more than that of adults [@yoshida2008], and both computational and empirical work suggest that this restricted viewpoint may be more effective for learning what objects and their labels than the comparable adult perspective [@yurovsky2012, @bambach2017]. Further, recent work also suggests dramatic changes in the child’s perspective over the first two years of life, as views transition from primarily containing close up view of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

Here, we directly ask whether the postural changes that infants’ experience as they reach their first birthday change the availability of the social information relevant for word learning. To do so, we recorded the visual experience of a group of infants and children using head-mounted cameras during a brief laboratory free-play session; children’s posture and their orientation to their caregiver were also recorded from a third-person perspective and hand-annotated. We capitalize on recent improvements in computer vision algorithms (@zhang2016, @cao2017realtime) that allow the automated detection of both faces and hands, and we analyze the frequency of both faces and hands in the child’s visual environment.

@@

\begin{table}[t]
  \caption{Model performance on gold standard generalization training set dataset. P, R, and F denote precision, recall, and F-score for each of the two samples. \label{tab:model_eval}}
  \begin{center}
    \begin{tabular}{l|ccc|ccc}
      \hline
       &  \multicolumn{3}{c|}{High-density} &  \multicolumn{3}{c}{Random} \\
      % \null Model & P & R & F & P & R & F  \\
      \hline
      % MTCNN & .84  & 1 &  .91 & .95 & .75 & .85   \\
      % OpenPose & .99 & .87 & .93 & .71 & .92 & .8 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}

>>>>

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(lme4)
library(gridExtra)
```
# Introduction
Children are remarkably skilled language learners, connecting arbitrary labels (“cup”) with specific visual concepts at a rapid pace through the first two years of life. However, children do not learn words in a vacuum but in a rich social environment, where social cues provided by speakers (e.g., eye-gaze) provide strong scaffolding for this learning process. Indeed, children’s ability to effectively process these social cues may be a key factor in their early language development. For example,in a longitudinal study, children’s level of joint engagement with their mother was found to predict both their receptive and productive vocabularies [@carpenter1998].  More recently, 10 month-olds who follow an adult’s gaze in an experimental context have larger vocabularies at 18 months [@brooks2005] and throughout the second year of life ]@brooks2008].

@@

One possibility is that these motor improvements have strong developmental cascades, impacting children’s emerging social, cognitive, and linguistic abilities [@iverson2010]. Indeed, these postural changes also impact how children interact with their mothers;  walking infants make different kinds of object-related bids for attention from their mothers than crawling infants, and tend to hear more action directed statements (e.g., “open it”) [@karasik2014].  More directly, in an observational study, @walle2014 found that children who were able to walk had both higher receptive and productive vocabularies.  On their account, children’s ability to stand and independently locomote may fundamentally change their ability to access the social information (e.g., faces, gaze) relative to children who are still crawling and sitting. In other words, the ability to access more detailed social information may allow infants to learn words quicker and more efficiently, facilitating language growth.

Recent work has begun to use egocentric, head-mounted cameras to document the visual experiences of infants and children — which even for walking children are radically different than the adult perspective (and not easily predicted by our own adult intuitions; [@clerkin2017;@franchak2011, @yoshida2008] ). Children’s views tend to be restricted and to be dominated by objects and hands much more than that of adults [@yoshida2008], and both computational and empirical work suggest that this restricted viewpoint may be more effective for learning what objects and their labels than the comparable adult perspective [ @bambach2017;@yurovsky2012]. Further, recent work also suggests dramatic changes in the child’s perspective over the first two years of life, as views transition from primarily containing close up view of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

Here, we directly ask whether the postural changes that infants’ experience as they reach their first birthday change the availability of the social information relevant for word learning. To do so, we recorded the visual experience of a group of infants and children using head-mounted cameras during a brief laboratory free-play session; children’s posture and their orientation to their caregiver were also recorded from a third-person perspective and hand-annotated. We capitalize on recent improvements in computer vision algorithms [@zhang2016, @cao2017realtime] that allow the automated detection of both faces and hands, and we analyze the frequency of both faces and hands in the child’s visual environment.

@@

\begin{table}[H]
  \caption{Model performance on gold standard generalization training set dataset. P, R, and F denote precision, recall, and F-score for each of the two samples. \label{tab:model_eval}}
  \begin{center}
    \begin{tabular}{l|ccc|ccc}
      \hline
       &  \multicolumn{3}{c|}{High-density} &  \multicolumn{3}{c}{Random} \\
      % \null Model & P & R & F & P & R & F  \\
      \hline
      % MTCNN & .84  & 1 &  .91 & .95 & .75 & .85   \\
      % OpenPose & .99 & .87 & .93 & .71 & .92 & .8 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}
